---
title: "colorpile"
author: "Mika Braginsky"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{colorpile}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
library(colorpiler)
library(knitr)
library(ggplot2)
library(shiny)
theme_set(theme_bw())
```

[Colorpile](https://github.com/ropenscilabs/colorpile) is a community-driven repository for color palettes. Color palettes are stored as `json` files containing the palette's colors and associated metadata. The [colorpiler](https://github.com/ropenscilabs/colorpiler) package lets users access and search these color palettes, use them in `ggplot2` plots and elsewhere, contribute their own palettes.

## Access and search

The `colorpile_metadata` function gives a data frame with all metadata about all of the color palettes in colorpile.

```{r}
head(colorpile_metadata())
```

To get only those palettes that match certain search criteria, use the `search_colorpile` function to filter palettes by author(s), github username, or type.

```{r}
search_colorpile(authors = c("Karthik Ram", "Ethan Schoonover"))
search_colorpile(authors = "Cynthia Brewer", type = "diverging")
```

Once you know the name of the color palette you want, use `colorpile_palette` to generate a function that gives a set of colors for a number of values.

```{r}
darjeeling <- colorpile_palette("Darjeeling")
darjeeling(3)
darjeeling(5)
```

## Viewing and plotting

Run the gadget `browse_colorpile` on a character vector of palette names to see what they look like.

```{r, eval=FALSE}
browse_colorpile(search_colorpile(github_user = "karthik"))
```

Or run the gadget `demo_colorpile` to see what a sample plot looks like with various palettes.

```{r, eval=FALSE}
demo_colorpile()
```

`colorpiler` provides color and fill scales for `ggplot2`. Just pass any `colorpiler` palette name to `scale_color_colorpile` or `scale_fill_colorpile`.

```{r, fig.width=6, fig.height=4}
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  scale_color_colorpile("Darjeeling")
```

## Contribute

To create a color palette, pass `create_palette` all of the metadata about your palette and character vector of its colors.

```{r, eval=FALSE}
create_palette(name = "best_ever",
               authors = "Alyssa P. Hacker",
               github_user = "ahacker",
               description = "Provides the best color palette of all time!",
               keywords = "awesome",
               colors = c("#000000", "#00FF00"),
               type = "qualitative")
```

This will create a `json` file specifying your palette, which you can then submit to colorpile by creating a pull request (stay tuned for this to happen automatically!).
